### 2014-08-30 fundamentals/qa.tex
now it builds

Multiple strategies collectively known a \emph{quality assurance} (QA) have 
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{verification and validation}
(V&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
\cite{sacks1989design}, testing, and others. V&V and UQ come from 
a distinctly computational science background while testing \emph{et al.} come from 
a software development bent.

>>>>

Multiple strategies collectively known a \emph{quality assurance} (QA) have 
been invented over the years to mitigate the structural and algorithmic errors
on the part of simulators themselves. These include \emph{verification and validation}
(V\&V) \cite{boehm1989software}, \emph{uncertainty quantification} (UQ) 
\cite{sacks1989design}, testing, and others. V\&V and UQ come from 
a distinctly computational science background while testing \emph{et al.} come from 
a software development bent.
